\begin{thebibliography}{99}

\bibitem{cognito}
Amazon Web Services. \textit{Amazon Cognito Developer Guide}. 2024. Truy cập tại: \texttt{https://docs.aws.amazon.com/cognito/latest/developerguide}. Ngày truy cập: 30/05/2026.

\bibitem{awsec2}
Amazon Web Services. \textit{Amazon EC2 User Guide for Linux Instances}. 2024. Truy cập tại: \texttt{https://docs.aws.amazon.com/AWSEC2/latest/UserGuide}. Ngày truy cập: 30/05/2026.

\bibitem{awsrds}
Amazon Web Services. \textit{Amazon RDS User Guide}. 2024. Truy cập tại: \texttt{https://docs.aws.amazon.com/AmazonRDS/latest/UserGuide}. Ngày truy cập: 30/05/2026.

\bibitem{awss3}
Amazon Web Services. \textit{Amazon S3 User Guide}. 2024. Truy cập tại: \texttt{https://docs.aws.amazon.com/AmazonS3/latest/userguide}. Ngày truy cập: 30/05/2026.

\bibitem{cloudfront}
Amazon Web Services. \textit{Amazon CloudFront Developer Guide}. 2024. Truy cập tại: \texttt{https://docs.aws.amazon.com/AmazonCloudFront/latest/DeveloperGuide}. Ngày truy cập: 30/05/2026.

\bibitem{alb}
Amazon Web Services. \textit{User Guide for Application Load Balancers}. 2024. Truy cập tại: \texttt{https://docs.aws.amazon.com/elasticloadbalancing/latest/application}. Ngày truy cập: 30/05/2026.

\bibitem{trello}
Atlassian. \textit{Trello — Manage Your Team's Projects From Anywhere}. 2024. Truy cập tại: \texttt{https://trello.com}. Ngày truy cập: 30/05/2026.

\bibitem{jira}
Atlassian. \textit{Jira Software — Plan, Track, and Release Great Software}. 2024. Truy cập tại: \texttt{https://www.atlassian.com/software/jira}. Ngày truy cập: 30/05/2026.

\end{thebibliography}
